\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\hypertarget{keywords}{%
\subsection{Keywords}\label{keywords}}

\emph{plumage}, \emph{dichromatism}, \emph{species recognition}

\hypertarget{background}{%
\section{Background}\label{background}}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{plumage-sexual-dichromatism}{%
\subsection{\texorpdfstring{\emph{Plumage sexual
dichromatism}}{Plumage sexual dichromatism}}\label{plumage-sexual-dichromatism}}

A total of N=77 \emph{Turdus} thrush species were sampled for plumage
spectral reflectance using from bird skins at the American Museum of
Natural History in New York City and the Field Museum in Chicago.
Reflectance measurements from 300-700nm were taken in triplicate for the
belly, breast, throat, crown and mantle plumage patches
{[}\protect\hyperlink{ref-anderssonQuantifyingColors2006}{1}{]} of each
individual bird skin. N=3 male and N=3 female individuals were measured
for most species (exceptions: \emph{Turdus lawrencii}, N=2 males and N=2
females; \emph{Turdus swalesi}, N=1 male and N=1 female). Reflectance
spectra were measured using a 400 μm fiber optic reflection probe fitted
with a rubber stopper to maintain a consistent measuring distance of 3
mm and area of 2 mm2 at a 90° angle to the surface of the feather patch.
Measurements were taken using a JAZ spectrometer with a pulsed-xenon
light source (Ocean Optics, Dunedin, USA) and all measurements were made
relative to a diffuse reflectance white standard (Spectralon WS-1-SL,
Labsphere, North Sutton NH, USA).

We used a receptor-noise limited visual model
{[}\protect\hyperlink{ref-vorobyevReceptorNoiseDeterminant1998}{2}{]} of
the European Blackbird (\emph{Turdus merula}) visual system
{[}\protect\hyperlink{ref-hartVisualPigmentsOil2000}{3}{]} in the
\emph{pavo} {[}\protect\hyperlink{ref-maiaPavoNewTools2019}{4}{]}⁠
package in R v4.0.0
{[}\protect\hyperlink{ref-rcoreteamLanguageEnvironmentStatistical2020}{5}{]}⁠
to calculate avian-perceived chromatic and achromatic visual contrast
(in units of ``Just-Noticeable Differences'',or JNDs) of male vs.~female
plumage patches for all sampled \emph{Turdus} species. Chromatic and
achromatic JNDs were calculated for male-female pairs within each
species (i.e., N=9 JND values calculated per patch for each species
where N=3 males and N=3 females sampled), and then JND values were
averaged for each species' respective plumage patches. Under ideal
laboratory conditions, a JND value of 1 is generally considered to be
the discriminable threshold past which an observer is predicted to be
able to perceive the two colors as different. However, natural light
environments vary both spatially and temporally
{[}\protect\hyperlink{ref-endlerColorLightForests1993}{6}{]}⁠, bringing
into question the accuracy of a JND=1 threshold for generalizing visual
contrast under natural conditions. Therefore, we calculated the total
number of sexually-dichromatic plumage patches per species (out of N=5
measured patches) as the number of plumage patches with average JND
values \textgreater{} 1, 2, or 3 to account for uncertainty in visual
discrimination thresholds due to variation in psychophysical and ambient
lighting conditions affecting the strength of between-sex plumage visual
contrast
{[}\protect\hyperlink{ref-kempIntegrativeFrameworkAppraisal2015}{7}{]}⁠.

\hypertarget{life-history-data}{%
\subsection{\texorpdfstring{\emph{Life History
Data}}{Life History Data}}\label{life-history-data}}

\hypertarget{breeding-timing-model}{%
\subsubsection{\texorpdfstring{\emph{Breeding Timing
Model}}{Breeding Timing Model}}\label{breeding-timing-model}}

We collected data on migration behavior and breeding season length from
\emph{Thrushes} {[}\protect\hyperlink{ref-clementThrushes2000}{8}{]} and
the \emph{Handbook of the Birds of the World}
{[}\protect\hyperlink{ref-delhoyoHandbookBirdsWorld2017}{9}{]}⁠. We
assigned three different kinds of migratory behavior: 1) \emph{full
migration} when a species description clearly stated that a species
``migrates'', 2) \emph{partial migration} when a species was described
to have ``altitudinal migration'', ``latitudinal migration'' or
``movement during non-breeding season'', or 3) \emph{sedentary} when
when a species was described as ``resident'' or ``sedentary''. Breeding
season length was defined as the number of months the species breeds.

\hypertarget{breeding-sympatry-model}{%
\subsubsection{\texorpdfstring{\emph{Breeding Sympatry
Model}}{Breeding Sympatry Model}}\label{breeding-sympatry-model}}

Species' breeding ranges were acquired from \emph{BirdLife
International}
{[}\protect\hyperlink{ref-birdlifeinternationalandhandbookofthebirdsoftheworldBirdSpeciesDistribution2018}{10}{]}⁠.
We calculated congener breeding range overlaps (as percentages) using
the \emph{letsR} package in R
{[}\protect\hyperlink{ref-vilelaLetsRNewPackage2015}{11}{]}⁠. We then
calculated the number of sympatric species as the number of congeners
with breeding ranges that overlap \textgreater30\% with the focal
species' breeding range
{[}\protect\hyperlink{ref-cooneySexualSelectionSpeciation2017}{12}{]}.

\hypertarget{breeding-spacing-model}{%
\subsubsection{\texorpdfstring{\emph{Breeding Spacing
Model}}{Breeding Spacing Model}}\label{breeding-spacing-model}}

Species' breeding range sizes (in km2) were acquired using the
\emph{BirdLife International} breeding range maps. Species' island
vs.~mainland residence was also determined using breeding ranges from
\emph{BirdLife International}. Mainland residence was assigned if the
species had a breeding range on any continent and Japan. Island
residence was assigned to species having a breeding range limited to a
non-continental landmass entirely surrounded by an oceanic body of
water.

\hypertarget{statistical-modeling}{%
\subsection{\texorpdfstring{\emph{Statistical
Modeling}}{Statistical Modeling}}\label{statistical-modeling}}

We used phylogenetically-corrected Bayesian multilevel logistic
regression models using the \emph{brms} v2.13.0 package
{[}\protect\hyperlink{ref-burknerBrmsPackageBayesian2017}{13}{]} in R
v4.0.0
{[}\protect\hyperlink{ref-rcoreteamLanguageEnvironmentStatistical2020}{5}{]}⁠
where responses, the number of sexually-dichromatic patches
\textgreater1, 2, and 3 chromatic and achromatic JNDs, were modeled as
binomial trials (N=5 plumage patch ``trials'') to test for associations
with breeding timing, breeding sympatry and breeding spacing. For all
phylogenetically-corrected models, we used the \emph{Turdus} phylogeny
from Nylander et al.~(2008)
{[}\protect\hyperlink{ref-nylanderAccountingPhylogeneticUncertainty2008}{14}{]}to
create a covariance matrix of species' phylogenetic relationships. All
models used a dataset of N=67 \emph{Turdus} species for which all data
were available.

Our \emph{breeding timing} models included the following predictors:
z-scores of breeding season length (mean centered and divided by one
standard deviation), migratory behavior (full migration as the reference
category versus partial migration or sedentary), and their interaction.
\emph{Breeding sympatry} models included the number of sympatric species
with greater than 30\% breeding range overlap as the only predictor of
the number of sexually-dichromatic plumage patches. \emph{Breeding
spacing} models included \(log_{e}\) transformed breeding range size
(km2) and breeding landmass (mainland as the reference category versus
island). We also ran null models (intercept only) for all responses. All
models' intercepts and response standard deviations were assigned a weak
prior (Student T: df = 3, location = 0, scale = 10), and predictor
coefficients were assigned flat priors. We ran each model for 6,000
iterations across 6 chains and assessed Markov Chain Monte Carlo (MCMC)
convergence using the Gelman-Rubin diagnostic (Rhat)
{[}\protect\hyperlink{ref-gelmanBayesianDataAnalysis2013}{15}{]}. We
then performed k-fold cross-validation
{[}\protect\hyperlink{ref-vehtariPracticalBayesianModel2017}{16}{]} to
refit each model \emph{K}=16 times. For each k-fold, the training
dataset included a randomly selected set of \(N- N\frac{1}{K}\) or N≈63
species, and the testing dataset included \(N\frac{1}{K}\) or N≈4
species not included in the training dataset. Finally, we compared
differences between the models' expected log pointwise predictive
densities (ELPD) to assess which model(s) best predicted the number of
sexually-dichromatic plumage patches
{[}\protect\hyperlink{ref-vehtariPracticalBayesianModel2017}{16}{]}⁠.

\hypertarget{results}{%
\section{Results}\label{results}}

We obtained N ≥ 4000 effective samples for each model parameter and all
models' Markov Chains (MCMC) successfully converged (Rhat = 1 for all
models' parameters).

\begin{table}[!h]

\caption{\label{tab:table01}Expected log pointwise predictive densities (ELPD) differences and
kfold information criterion values of models.}
\centering
\resizebox{\linewidth}{!}{
\renewcommand{\arraystretch}{1.5}
\begin{tabular}[t]{llllll}
\toprule
\multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{4}{l}{Model} \\
\cmidrule(l{3pt}r{3pt}){3-6}
Plumage Metric & JND Threshold & Breeding Sympatry & Breeding Timing & Breeding Spacing & Intercept Only\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Achromatic}}\\
\hspace{1em} & 1 JND & 0 ± 0 (-122.17 ± 0.67) & -2.51 ± 2.49 (-124.68 ± 2.38) & -2.59 ± 1.01 (-124.76 ± 1.04) & -21.69 ± 7.36 (-143.87 ± 7.51)\\
\hspace{1em} & 2 JND & 0 ± 0 (-98.94 ± 7.56) & -1.19 ± 3.95 (-100.13 ± 9.22) & -0.7 ± 1.34 (-99.64 ± 7.92) & -52.42 ± 12.67 (-151.36 ± 13.4)\\
\hspace{1em} & 3 JND & -0.04 ± 1.4 (-85.4 ± 8.91) & -1.7 ± 4.41 (-87.07 ± 10.71) & 0 ± 0 (-85.37 ± 8.76) & -28.54 ± 10.02 (-113.91 ± 13.65)\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Chromatic}}\\
\hspace{1em} & 1 JND & 0 ± 0 (-115.75 ± 2.95) & -5.67 ± 3.55 (-121.42 ± 2.28) & -2.73 ± 3.4 (-118.49 ± 2.67) & -14.8 ± 7.22 (-130.55 ± 7.05)\\
\hspace{1em} & 2 JND & 0 ± 0 (-88.47 ± 8.77) & -3.8 ± 4.46 (-92.27 ± 10.01) & -3.32 ± 5.29 (-91.79 ± 10.91) & -50.53 ± 14.49 (-139 ± 16.77)\\
\hspace{1em} & 3 JND & 0 ± 0 (-62.77 ± 10.41) & -8 ± 4.32 (-70.77 ± 12.29) & -4.43 ± 3.9 (-67.2 ± 11.72) & -47.63 ± 15.34 (-110.4 ± 20.01)\\
\bottomrule
\end{tabular}}
\end{table}

\newpage
\begin{landscape}
\begin{table}

\caption{\label{tab:table02}Model predictor effect estimates (posterior median log-odds and 90\% credible interval) on the
  presence of a plumage patch with achromatic or chromatic visual contrast values $>$
  1, 2, and 3 JND. Model effects with a probability of direction (pd) value $\geq$ 0.90
  are bolded in \textcolor{red}{\textbf{red}} for a negative effect and \textcolor{blue}{\textbf{blue}} for a positive effect on
  plumage dichromatism.}
\centering
\resizebox{\linewidth}{!}{
\renewcommand{\arraystretch}{1.5}
\begin{tabular}[t]{llllllll}
\toprule
Model & Parameter & Achromatic, 1 JND & Achromatic, 2 JND & Achromatic, 3 JND & Chromatic, 1 JND & Chromatic, 2 JND & Chromatic, 3 JND\\
\midrule
\addlinespace[0.3em]
\multicolumn{1}{l}{\textbf{Breeding Timing}}\\
 & Intercept & \textcolor{black}{-1.16 (-3.87, 1.67), pd = 0.76} & \textcolor{red}{\textbf{-8.36 (-16.28, -0.62), pd = 0.98}} & \textcolor{red}{\textbf{-7.81 (-14.83, -1.66), pd = 0.99}} & \textcolor{black}{-0.88 (-2.98, 1.03), pd = 0.78} & \textcolor{red}{\textbf{-7.21 (-15.29, 0.55), pd = 0.95}} & \textcolor{red}{\textbf{-12.71 (-28.03, 0.31), pd = 0.96}}\\
 & Breeding Season Length & \textcolor{black}{-0.06 (-0.62, 0.56), pd = 0.57} & \textcolor{red}{\textbf{-2.26 (-4.72, 0.05), pd = 0.97}} & \textcolor{red}{\textbf{-1.39 (-3.56, 0.4), pd = 0.91}} & \textcolor{black}{-0.12 (-0.59, 0.34), pd = 0.66} & \textcolor{red}{\textbf{-1.99 (-4.64, 0.35), pd = 0.94}} & \textcolor{black}{-2.5 (-8.12, 2.21), pd = 0.83}\\
 & Partial Migration vs. No Migration & \textcolor{black}{-0.04 (-1.16, 1.01), pd = 0.53} & \textcolor{black}{1.41 (-1.2, 4.12), pd = 0.83} & \textcolor{black}{1.29 (-0.82, 3.57), pd = 0.85} & \textcolor{blue}{\textbf{0.79 (-0.06, 1.59), pd = 0.94}} & \textcolor{black}{1.9 (-0.87, 4.9), pd = 0.88} & \textcolor{blue}{\textbf{4.26 (-1.13, 10.99), pd = 0.92}}\\
 & Full Migration vs. No Migration & \textcolor{blue}{\textbf{1.6 (-0.05, 3.19), pd = 0.96}} & \textcolor{blue}{\textbf{4.2 (1.16, 7.5), pd = 0.99}} & \textcolor{blue}{\textbf{3.11 (0.46, 5.73), pd = 0.98}} & \textcolor{black}{0.83 (-0.37, 1.99), pd = 0.88} & \textcolor{blue}{\textbf{4.39 (1.03, 8.14), pd = 0.99}} & \textcolor{blue}{\textbf{5.46 (-0.68, 12.61), pd = 0.95}}\\
 & Breeding Season Length x Partial Migration & \textcolor{black}{0.29 (-0.73, 1.37), pd = 0.68} & \textcolor{blue}{\textbf{3.03 (-0.14, 6.38), pd = 0.96}} & \textcolor{blue}{\textbf{2.11 (-0.27, 4.69), pd = 0.94}} & \textcolor{black}{0.33 (-0.43, 1.14), pd = 0.76} & \textcolor{blue}{\textbf{2.2 (-0.82, 5.53), pd = 0.9}} & \textcolor{black}{3.54 (-2.58, 11.13), pd = 0.85}\\
 & Breeding Season Length x Full Migration & \textcolor{blue}{\textbf{1.58 (-0.4, 3.68), pd = 0.9}} & \textcolor{blue}{\textbf{4.19 (-0.53, 9.34), pd = 0.93}} & \textcolor{black}{2.8 (-1.3, 6.72), pd = 0.89} & \textcolor{black}{0.52 (-1.16, 2.12), pd = 0.7} & \textcolor{blue}{\textbf{5.08 (-0.18, 11.12), pd = 0.95}} & \textcolor{black}{6.07 (-4.27, 17.43), pd = 0.85}\\
 & Phylogenetic Signal λ, Median (90\% Credible Interval) & \textcolor{black}{0.29 (0.16, 0.43)} & \textcolor{black}{0.72 (0.56, 0.86)} & \textcolor{black}{0.61 (0.42, 0.8)} & \textcolor{black}{0.17 (0.08, 0.28)} & \textcolor{black}{0.74 (0.57, 0.88)} & \textcolor{black}{0.89 (0.77, 0.97)}\\
\addlinespace[0.3em]
\multicolumn{1}{l}{\textbf{Breeding Spacing}}\\
\hspace{1em} & Intercept & \textcolor{black}{-1.94 (-6.01, 2.01), pd = 0.8} & \textcolor{red}{\textbf{-9.77 (-20.11, 0.89), pd = 0.95}} & \textcolor{red}{\textbf{-10.31 (-19.2, -1.98), pd = 0.98}} & \textcolor{black}{-0.67 (-3.63, 2.27), pd = 0.65} & \textcolor{red}{\textbf{-8.32 (-18.86, 2.03), pd = 0.92}} & \textcolor{red}{\textbf{-12.87 (-30.57, 4.41), pd = 0.91}}\\
\hspace{1em} & Island vs. Mainland & \textcolor{black}{0.08 (-1.38, 1.57), pd = 0.54} & \textcolor{black}{-0.64 (-4.43, 2.88), pd = 0.61} & \textcolor{black}{-0.09 (-3.02, 2.96), pd = 0.52} & \textcolor{red}{\textbf{-1.3 (-2.45, -0.12), pd = 0.97}} & \textcolor{black}{-3.39 (-8.67, 1.38), pd = 0.89} & \textcolor{black}{-3.26 (-12.57, 4.21), pd = 0.77}\\
\hspace{1em} & Breeding Range Size & \textcolor{black}{0.08 (-0.13, 0.28), pd = 0.75} & \textcolor{black}{0.21 (-0.27, 0.7), pd = 0.77} & \textcolor{black}{0.26 (-0.14, 0.66), pd = 0.87} & \textcolor{black}{0.02 (-0.14, 0.18), pd = 0.58} & \textcolor{black}{0.21 (-0.29, 0.72), pd = 0.77} & \textcolor{black}{0.23 (-0.62, 1.1), pd = 0.69}\\
\hspace{1em} & Phylogenetic Signal λ, Median (90\% Credible Interval) & \textcolor{black}{0.27 (0.15, 0.41)} & \textcolor{black}{0.71 (0.56, 0.85)} & \textcolor{black}{0.6 (0.42, 0.77)} & \textcolor{black}{0.15 (0.07, 0.25)} & \textcolor{black}{0.72 (0.55, 0.86)} & \textcolor{black}{0.85 (0.71, 0.95)}\\
\addlinespace[0.3em]
\multicolumn{1}{l}{\textbf{Breeding Sympatry}}\\
\hspace{1em} & Intercept & \textcolor{red}{\textbf{-0.9 (-3.45, 1.76), pd = 0.72}} & \textcolor{red}{\textbf{-6.89 (-14.7, -0.02), pd = 0.95}} & \textcolor{red}{\textbf{-6.74 (-13.39, -1.09), pd = 0.98}} & \textcolor{red}{\textbf{-1.38 (-3.25, 0.3), pd = 0.91}} & \textcolor{red}{\textbf{-6.34 (-13.61, 0.11), pd = 0.95}} & \textcolor{red}{\textbf{-11.29 (-22.79, -1.24), pd = 0.98}}\\
 & Number of Sympatric Species 
\hspace{1em} (≥ 30\% Breeding Range Overlap) & \textcolor{black}{0.03 (-0.18, 0.24), pd = 0.61} & \textcolor{black}{0.14 (-0.31, 0.56), pd = 0.71} & \textcolor{black}{0.12 (-0.27, 0.49), pd = 0.71} & \textcolor{blue}{\textbf{0.34 (0.17, 0.51), pd = 0.99}} & \textcolor{blue}{\textbf{0.46 (0.01, 0.92), pd = 0.96}} & \textcolor{blue}{\textbf{0.75 (0.03, 1.5), pd = 0.97}}\\
\hspace{1em} & Phylogenetic Signal λ, Median (90\% Credible Interval) & \textcolor{black}{0.26 (0.14, 0.39)} & \textcolor{black}{0.7 (0.54, 0.83)} & \textcolor{black}{0.59 (0.41, 0.77)} & \textcolor{black}{0.13 (0.06, 0.23)} & \textcolor{black}{0.69 (0.52, 0.83)} & \textcolor{black}{0.82 (0.67, 0.94)}\\
\bottomrule
\end{tabular}}
\end{table}
\end{landscape}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\hypertarget{ref-anderssonQuantifyingColors2006}{}%
\CSLLeftMargin{1. }
\CSLRightInline{Andersson S, Prager M. 2006 Quantifying {Colors}. In
\emph{Bird coloration, {Volume} 1: {Mechanisms} and {Measurements}} (eds
GE Hill, KJ McGraw), pp. 76--77. {Cambridge, MA}: {Harvard University
Press}. }

\leavevmode\hypertarget{ref-vorobyevReceptorNoiseDeterminant1998}{}%
\CSLLeftMargin{2. }
\CSLRightInline{Vorobyev M, Osorio D. 1998 Receptor noise as a
determinant of colour thresholds. \emph{Proceedings. Biological sciences
/ The Royal Society} \textbf{265}, 351--8.
(doi:\href{https://doi.org/10.1098/rspb.1998.0302}{10.1098/rspb.1998.0302})}

\leavevmode\hypertarget{ref-hartVisualPigmentsOil2000}{}%
\CSLLeftMargin{3. }
\CSLRightInline{Hart NS, Partridge JC, Cuthill IC, Bennett AT. 2000
Visual pigments, oil droplets, ocular media and cone photoreceptor
distribution in two species of passerine bird: The blue tit ({Parus}
caeruleus {L}.) And the blackbird ({Turdus} merula {L}.). \emph{Journal
of comparative physiology. A, Sensory, neural, and behavioral
physiology} \textbf{186}, 375--387.
(doi:\href{https://doi.org/10.1007/s003590050437}{10.1007/s003590050437})}

\leavevmode\hypertarget{ref-maiaPavoNewTools2019}{}%
\CSLLeftMargin{4. }
\CSLRightInline{Maia R, Gruson H, Endler JA, White TE. 2019 Pavo 2:
{New} tools for the spectral and spatial analysis of colour in r.
\emph{Methods in Ecology and Evolution} \textbf{10}, 1097--1107.
(doi:\href{https://doi.org/10.1111/2041-210X.13174}{10.1111/2041-210X.13174})}

\leavevmode\hypertarget{ref-rcoreteamLanguageEnvironmentStatistical2020}{}%
\CSLLeftMargin{5. }
\CSLRightInline{R Core Team. 2020 \emph{R: {A Language} and
{Environment} for {Statistical Computing}}. {Vienna, Austria}: {R
Foundation for Statistical Computing}. }

\leavevmode\hypertarget{ref-endlerColorLightForests1993}{}%
\CSLLeftMargin{6. }
\CSLRightInline{Endler JA, Monographs E, Feb N. 1993 The {Color} of
{Light} in {Forests} and {Its Implications}. \emph{Ecological
Monographs} \textbf{63}, 1--27.
(doi:\href{https://doi.org/10.2307/2937121}{10.2307/2937121})}

\leavevmode\hypertarget{ref-kempIntegrativeFrameworkAppraisal2015}{}%
\CSLLeftMargin{7. }
\CSLRightInline{Kemp DJ, Herberstein ME, Fleishman LJ, Endler JA,
Bennett ATD, Dyer AG, Hart NS, Marshall J, Whiting MJ. 2015 An
{Integrative Framework} for the {Appraisal} of {Coloration} in {Nature}.
\emph{The American Naturalist} \textbf{185}, 705--724.
(doi:\href{https://doi.org/10.1086/681021}{10.1086/681021})}

\leavevmode\hypertarget{ref-clementThrushes2000}{}%
\CSLLeftMargin{8. }
\CSLRightInline{Clement P, Hathway R. 2000 \emph{Thrushes}. {London}:
{A\&C Black Publishers Ltd}. }

\leavevmode\hypertarget{ref-delhoyoHandbookBirdsWorld2017}{}%
\CSLLeftMargin{9. }
\CSLRightInline{del Hoyo J, Elliott A, Sargatal J, Christie DA, de Juana
E. 2017 \emph{Handbook of the birds of the world alive}. }

\leavevmode\hypertarget{ref-birdlifeinternationalandhandbookofthebirdsoftheworldBirdSpeciesDistribution2018}{}%
\CSLLeftMargin{10. }
\CSLRightInline{BirdLife International and Handbook of the Birds of the
World. 2018 \emph{Bird species distribution maps of the world. {Version}
2018.1.} }

\leavevmode\hypertarget{ref-vilelaLetsRNewPackage2015}{}%
\CSLLeftMargin{11. }
\CSLRightInline{Vilela B, Villalobos F. 2015 {letsR}: A new {R} package
for data handling and analysis in macroecology. \emph{Methods in Ecology
and Evolution} \textbf{6}, 1229--1234.
(doi:\href{https://doi.org/10.1111/2041-210X.12401}{10.1111/2041-210X.12401})}

\leavevmode\hypertarget{ref-cooneySexualSelectionSpeciation2017}{}%
\CSLLeftMargin{12. }
\CSLRightInline{Cooney CR, Tobias JA, Weir JT, Botero CA, Seddon N. 2017
Sexual selection, speciation and constraints on geographical range
overlap in birds. \emph{Ecology Letters} \textbf{20}, 863--871.
(doi:\href{https://doi.org/10.1111/ele.12780}{10.1111/ele.12780})}

\leavevmode\hypertarget{ref-burknerBrmsPackageBayesian2017}{}%
\CSLLeftMargin{13. }
\CSLRightInline{Bürkner PC. 2017 Brms: {An R} package for {Bayesian}
multilevel models using {Stan}. \emph{Journal of Statistical Software}
\textbf{80}, 1--28.
(doi:\href{https://doi.org/10.18637/jss.v080.i01}{10.18637/jss.v080.i01})}

\leavevmode\hypertarget{ref-nylanderAccountingPhylogeneticUncertainty2008}{}%
\CSLLeftMargin{14. }
\CSLRightInline{Nylander JAA, Olsson U, Alström P, Sanmartín I. 2008
Accounting for phylogenetic uncertainty in biogeography: {A} bayesian
approach to dispersal-vicariance analysis of the thrushes ({Aves}:
{Turdus}). \emph{Systematic Biology} \textbf{57}, 257--268.
(doi:\href{https://doi.org/10.1080/10635150802044003}{10.1080/10635150802044003})}

\leavevmode\hypertarget{ref-gelmanBayesianDataAnalysis2013}{}%
\CSLLeftMargin{15. }
\CSLRightInline{Gelman A, Carlin JB, Stern HS, Dunson DB, Vehtari A,
Rubin DB. 2013 \emph{Bayesian data analysis, third edition}. Third.
{Boca Raton, FL}: {CRC Press}.
(doi:\href{https://doi.org/10.1201/b16018}{10.1201/b16018})}

\leavevmode\hypertarget{ref-vehtariPracticalBayesianModel2017}{}%
\CSLLeftMargin{16. }
\CSLRightInline{Vehtari A, Gelman A, Gabry J. 2017 Practical {Bayesian}
model evaluation using leave-one-out cross-validation and {WAIC}.
\emph{Statistics and Computing} \textbf{27}, 1413--1432.
(doi:\href{https://doi.org/10.1007/s11222-016-9696-4}{10.1007/s11222-016-9696-4})}

\end{CSLReferences}
